Secure Composition of Robust and Optimising Compilers

### 2023-07-12 popl/main.tex
fix

\gls{ms} is a security property obtained by composing \gls{sms}, which ensures array accesses are all within bounds, and \gls{tms}, which ensures pointers are only used when they are valid~\cite{azevedo2018meaningsofms}\MP{more cits}.
\gls{cct} is a security property that ensures sensitive data is not leaked via timing side-channels~\cite{kocher1996timing}.
Together, \gls{sms}, \gls{tms} and \gls{cct} yield \gls{msscct}, which is the gold standard of security properties for secure applications: programs attaining \gls{msscct} do not leak sensitive data neither through erroneous memory accesses, nor through timing side-channels.
As discussed in \Cref{ex:strncpy}, these security properties can be enforced by compiler passes~\cite{bond2017vale,almeida2017jasmin}, to ensure programmers need not be aware of the various architectural details where their code will run.

>>>>

\gls{ms} is a security property obtained by composing \gls{sms}, which ensures array accesses are all within bounds, and \gls{tms}, which ensures pointers are only used when they are valid~\cite{azevedo2018meaningsofms,jim2002cyclone,necula2005ccured,nagarakatte2010cets,nagarakatte2009soft,akritidis2009baggy,michael2023mswasm}.
\gls{cct} is a security property that ensures sensitive data is not leaked via timing side-channels~\cite{kocher1996timing}.
Together, \gls{sms}, \gls{tms} and \gls{cct} yield \gls{msscct}, which is the gold standard of security properties for secure applications: programs attaining \gls{msscct} do not leak sensitive data neither through erroneous memory accesses, nor through timing side-channels.
As discussed in \Cref{ex:strncpy}, these security properties can be enforced by compiler passes~\cite{bond2017vale,almeida2017jasmin}, to ensure programmers need not be aware of the various architectural details where their code will run.
